% !TEX root = ../AC52010-Report.tex
%
\pdfbookmark[0]{Abstract}{Abstract}
\chapter*{Abstract}
\label{sec:abstract}
\vspace*{-10mm}

%\blindtext

The Information Services Division (ISD) is a division of National Services Scotland, part of NHS Scotland.  ISD provides health information, health intelligence, statistical services and advice that support the NHS in progressing quality improvement in health and care and facilitates robust planning and decision making.
 
The Scottish Routes from Diagnosis (SRfD) project forms part of the successful Macmillan Cancer Care/ISD partnership.  SRfD uses routinely collected health data and aims to quantitatively describe the pathways patients follow after diagnosis with cancer in Scotland.  SRfD is an adapted framework based on the English Routes from Diagnosis.
 
The key objective of this project will to be use the data to identify these pathways and to develop an analytical tool or dashboard (using Tableau and/or R Shiny) to visualise the pathways.  The dashboard should allow users to understand the different routes patients take following a cancer diagnosis in Scotland, through treatment and future quality of life.  Further objectives will be to develop accompanying documentation and training materials and to present the work to colleagues.
 
An anonymised dataset of circa 30,000 cases will be available to the student.  The dataset will include cohorts of patients diagnosed with Breast, Lung, Colorectal or Prostate cancer in Scotland and will contain healthcare information and demographic factors.  Data relating to the patient’s diagnosis, treatment and outcomes will be also included.  
 

\vspace*{20mm}

%{\usekomafont{chapter}Abstract (different language)}\label{sec:abstract-diff} \\

%\blindtext
